---
title: "GAV Families"
author: "Cheryl"
date: "03 December 2019"
output: html_document
---

#All Cohorts Families

#To view GAV loads of all families using ggplot2
```{r}
library(tidyverse) ## Do this everytime you restart R and need it
library(ggplot2)
```

#Import dataset of all cohorts families
```{r}
allfams <- read_csv("https://raw.githubusercontent.com/cheryltky/ViralTransmission/master/Working%20Files/allcohortfamsv2.csv")
head(allfams)
summary(allfams)
str(allfams)
```

# Make PrawnID, Class, Age, FamID , IntFamID as factors

```{r}
allfams <- allfams %>% mutate_if(is.character, as.factor)
allfams$IntFamID <- as.factor(allfams$IntFamID)
allfams$PrawnID <- as.factor(allfams$PrawnID)
allfams$Class <- as.factor(allfams$Class)
allfams$Age <- as.factor(allfams$Age)
allfams$Cohort <- as.factor(allfams$Cohort)
allfams$FamID <- as.factor(allfams$FamID)
str(allfams)
summary(allfams)
```

##Scatterplot by families

```{r}
ggplot(allfams , aes(IntFamID , GAV)) +
  geom_point() +
  theme_classic()
```

##Jitterplot by families
```{r}
ggplot(allfams , aes(IntFamID , GAV)) +
  geom_jitter(width = 0.2) +
  aes(color = Age , shape = Class ) +
  labs( title = "All families GAV loads")

allcohortfams <- ggplot(allfams , aes(IntFamID , GAV)) +
  geom_jitter(width = 0.2) +
  aes(color = Age , shape = Class ) +
  labs( title = "All Families GAV Loads",
        x = "Family" , 
        y = "GAV RNA copies/ug TNA")

allcohortfams
ggsave("allcohortfams.png" , allcohortfams , width = 15, height = 10 , dpi = 300)
```


## Import dataset for top 10 families cohort 201604

```{r}
toptenfams <- read_csv("https://raw.githubusercontent.com/cheryltky/ViralTransmission/master/Working%20Files/20160204topfams.csv")
head(toptenfams)
str(toptenfams)
summary(toptenfams)
```

## Make PrawnID, Class, Age, FamID , IntFamID as factors
```{r}
toptenfams$IntFamID <- as.factor(toptenfams$IntFamID)
toptenfams$PrawnID <- as.factor(toptenfams$PrawnID)
toptenfams$Class <- as.factor(toptenfams$Class)
toptenfams$Age <- as.factor(toptenfams$Age)
toptenfams$Cohort <- as.factor(toptenfams$Cohort)
toptenfams$FamID <- as.factor(toptenfams$FamID)
str(toptenfams)
summary(toptenfams)
```

## Scatterplot of 201604 top families
```{r}
ggplot(toptenfams , aes(IntFamID, GAV)) +
  geom_point() + 
  theme_classic()
```

## Jitterplot of top 201604 families
```{r}
Topfams20160204 <- ggplot(toptenfams , aes(IntFamID, GAV)) +
  geom_jitter(width = 0.25) +
  aes(color = Age, shape = Class) +
  labs(title = "Top 11 20160204 GAV families",
       x = "Family ID",
       y = "Log10GAV copies/ug TNA") +
  theme_bw()



ggsave("Topfams20160204.png", Topfams20160204 , width = 15, height = 10, dpi = 300)
  
```

## Import dataset for cohort 3: 201701 top 10 fams
```{r}
cohort3topfams <- read_csv("https://raw.githubusercontent.com/cheryltky/ViralTransmission/master/Working%20Files/201701top10fams.csv")
head(cohort3topfams)
str(cohort3topfams)
summary(cohort3topfams)
```

## Jitterplot for Cohort 3: 201701 top 10 fams
```{r}
cohort3topfams <- ggplot(cohort3topfams, aes(IntFamID, GAV)) +
  geom_jitter(width = 0.25) +
  aes(color = Age, shape = Class) +
  labs(title = "Cohort 3 Top 10 GAV Families" ,
       x = "Family ID",
       y = "Log10GAVcopies/ug TNA") +
  theme_bw()

cohort3topfams
ggsave("Topcohort3fams.png", cohort3topfams, width = 15, height = 10, dpi = 300)
```

## Import dataset for Cohort 1: 201602 top 10 fams
```{r}
cohort1topfams <-read_csv("https://raw.githubusercontent.com/cheryltky/ViralTransmission/master/Working%20Files/201602topfams.csv")
head(cohort1topfams)
str(cohort1topfams)
summary(cohort1topfams)
```

## Make PrawnID, Class, Age, FamID , IntFamID as factors
```{r}
cohort1topfams$PrawnID <- as.factor(cohort1topfams$PrawnID)
cohort1topfams$Class <- as.factor(cohort1topfams$Class)
cohort1topfams$Age <- as.factor(cohort1topfams$Age)
cohort1topfams$Cohort <- as.factor(cohort1topfams$Cohort)
cohort1topfams$FamID <- as.factor(cohort1topfams$FamID)
str(cohort1topfams)
summary(cohort1topfams)
```

## Jitterplot of cohort 1: 201602 top 10 fams
```{r}
cohort1top10fams <- ggplot(cohort1topfams, aes(IntFamID, GAV)) +
  geom_jitter(width = 0.25) +
  aes(color = Class, shape = Class) +
  labs(title = "Cohort 1 Top GAV Families",
       x = "Family ID",
       y = "Log10GAVcopies/ug TNA") +
  theme_bw()

cohort1top10fams
```

##Import data for top 10 families per cohort 
```{r}
allcohorttopfams <- read_csv("https://raw.githubusercontent.com/cheryltky/ViralTransmission/master/Working%20Files/allcohortstop30fams.csv")
head(allcohorttopfams)
str(allcohorttopfams)
summary(allcohorttopfams)
```

## Make PrawnID, Class, Age, FamID , IntFamID as factors
```{r}
allcohorttopfams$PrawnID <- as.factor(allcohorttopfams$PrawnID)
allcohorttopfams$Class <- as.factor(allcohorttopfams$Class)
allcohorttopfams$Age <- as.factor(allcohorttopfams$Age)
allcohorttopfams$Cohort <- as.factor(allcohorttopfams$Cohort)
allcohorttopfams$FamID <- as.factor(allcohorttopfams$FamID)
```

## Make jitterplot for all cohorts top fams
```{r}
allcohorttopfams <- ggplot(allcohorttopfams, aes(CohortFamID , GAV)) +
  geom_jitter(width = 
```

